A Study of Common Bug Fix Patterns in Rust

### 2022-11-25 related.tex
added more to related

We would characterize our work as the Rust version of what was done in~\cite{hanam2016discovering} and~\cite{yang2022mining}. Like~\cite{hanam2016discovering}, we used DBSCAN to cluster fixes. However, our novel program embedding approach differs from what they did. In~\cite{hanam2016discovering}, they introduced Feature Properties table, which is a categorization for program elements. Embedding programs based on this table resulted in a order-sensitive embedding, however, it made the datapoints sparse. Moreover, like~\cite{yang2022mining}, we introduced patterns in two different categories. In our case there were general and language-specific patterns; for Rust, the language-specific patterns were related to the borrow checker (BC patterns). However, as opposed to our paper, \cite{yang2022mining} needed to do a much more elaborate manual analysis, as they had only collected general information about the single hunk changes (e.g. the number of variables, or arguments).

>>>>

We would characterize our work as the Rust version of what was done in~\cite{hanam2016discovering} and~\cite{yang2022mining}. Like~\cite{hanam2016discovering}, we used DBSCAN to cluster fixes. Moreover, similar to~\cite{yang2022mining}, we introduced patterns in two different categories. In our case there were general and language-specific patterns; for Rust, the language-specific patterns were related to the borrow checker (BC patterns). However, unlike our paper, \cite{yang2022mining} needed to do a much more elaborate manual analysis, as they had only collected general information about the single hunk changes (e.g. the number of variables, or arguments).

\subsection{Code Embedding}

Recent advances in deep learning has motivated researchers to build models for various types of data. A common step for building these machine learning models is to create a numerical representation of data, so that it can be fed into the model. To realize this mapping in natural languages, the researchers have proposed methods to embed word information in fixed size vectors. This process is known as word embedding. As programming languages are not that different from natural languages~\citep{hindle2016naturalness}, similar mappings have been suggested for computer programs~\citep{chen2019literature}.

\cite{alon2019code2vec} presented code2vec, a nueral model for representing code snippets as fixed size vectors. In their approach, they extracted flattened paths from the AST, and stored all the leaf-to-leaf paths. The intuition behind this decision was that leaf-to-leaf paths tend to encode more semantic information than root-to-leaf paths. They associated a fixed size vector to each path and fed them as inputs to a neural network that learns how to aggregate all these paths to a single embedding. Our code embedding approach is simpler than code2vec, as we seek a less sophisticated goal than them---bug patterns clustering instead of method name prediction. Moreover, unlike us, code2vec does not offer a general code embedding methods, since the final embedding depends on the output layer of the neural network. That is, if we change the goal of method name prediction, the embeddings would be completely different. Also, our code embedding has actual interpretability as our columns are associated with non terminals. In code2vec, the dimensions of the final vector is a parameter of the system and to no extent is related to the underlying programming language.

Our work tends to be more similar to that of \cite{hanam2016discovering}. However, our novel program embedding approach might differ from what they did on certain key decisions. In~\cite{hanam2016discovering}, they introduced the Feature Properties table, which is a categorization for program elements. Embedding programs based on this table resulted in an order-sensitive embedding, however, it made the datapoints sparse.
